---
title: "Covid-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE ,message = FALSE, warning = FALSE)
```
#
### Data pre-processing
###
##### Data import
```{r echo=TRUE}
library(dplyr)
library(tidyr)
library(forcats)
library(ggplot2)
library(readr)
library(directlabels)
library(knitr)
library(zoo)

full_data_corona <- read_csv("https://covid.ourworldindata.org/data/owid-covid-data.csv")

who_region_original <- read_csv("C:/Users/caioe/Downloads/who-regions.csv")

who_region <- who_region_original %>% 
  select(Entity, Code,'WHO region') %>% 
  rename(who_region = "WHO region") %>% 
  group_by(Entity, Code,who_region)

full_data_corona <- full_data_corona %>% 
  left_join(who_region, by = c("location" = "Entity")) %>% 
  mutate(rate = total_deaths/total_cases)
```

```{r}
#library(extrafont)

#download.file("http://simonsoftware.se/other/xkcd.ttf",
#              dest="xkcd.ttf", mode="wb")
#system("mkdir ~/.fonts")
#system("cp xkcd.ttf  ~/.fonts")
#font_import(paths = "~/.fonts", pattern="[X/x]kcd")
#fonts()
#loadfonts()
```


```{r}
cases <- full_data_corona %>% 
  filter(total_cases >= 100) %>% 
  group_by(location) %>% 
  arrange(date,location) %>% 
  mutate(day = row_number())

deaths <- full_data_corona %>% 
  filter(total_deaths >= 5) %>% 
  group_by(location) %>% 
  arrange(date,location) %>% 
  mutate(day = row_number())

tests <- full_data_corona %>% 
  filter(total_tests > 0) %>% 
  group_by(location) %>% 
  arrange(date,location) %>% 
  mutate(day = row_number())

day_compare <- cases %>% 
  filter(day == max(day))
  
max_cases <- full_data_corona %>% 
  filter(total_cases > 100, location != "World") %>% 
  group_by(location) %>% 
  arrange(date,location) %>% 
  mutate(max_cases_day = row_number()) %>%
  filter(new_cases == max(new_cases)) %>% 
  rename(max_date = date,
         max_new_cases = new_cases,
         max_new_deaths = new_deaths,
         max_total_cases = total_cases,
         max_total_deaths = total_deaths) %>% 
  select(max_date,
         location,
         max_new_cases,
         max_new_deaths,
         max_total_cases,
         max_total_deaths,
         max_cases_day)
```

```{r}
cases %>% 
  filter(date == max(date)) %>% 
  select(location,
         who_region,
         day,
         new_cases,
         total_cases,
         new_deaths,
         total_deaths,
         rate,
         total_cases_per_million,
         total_deaths_per_million) %>% 
  arrange(-total_deaths) %>%
  mutate(rate = round(rate*100,1),
         total_cases_per_million = round(total_cases_per_million, 1),
         total_deaths_per_million = round(total_deaths_per_million, 1)) %>% 
  head(50) %>% 
  kable(format = "markdown")

```

#### Days compare

```{r echo=TRUE, fig.width=7, fig.height=7}
day_compare %>% 
  filter(!location %in% c("China", "World"),
         total_cases >= 10000) %>% 
  ggplot(mapping = aes(x = day, 
                       y = fct_reorder(location,day), 
                       size = total_deaths_per_million, 
                       colour = who_region)) +
  geom_point(stat = "identity") +
  theme(axis.text.y = element_text(size=10), 
        axis.title.y = element_blank(),
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7)) +
  facet_grid(rows = vars(who_region),
             scales = "free",
             space = "free")
```

#### Difference between actual and max case day

```{r echo=TRUE, fig.width=7, fig.height=7}
day_compare %>% 
  filter(!location %in% c("China","World"),
         total_cases >= 10000) %>%
  left_join(max_cases, by = c("location" = "location")) %>% 
  pivot_longer(c(day,max_cases_day),
               names_to = "type",
               values_to = "day") %>% 
  ggplot(mapping = aes(x = day,
                       y = fct_reorder(location,day), 
                       colour = who_region)) +
  geom_point(aes(shape = type), 
             size = 2.5) + 
  geom_line(alpha = 0.5, 
            linetype = "dashed", 
            size = 1) +
  scale_x_continuous(breaks = seq(0, 100, by = 15)) +
  theme(axis.text.y = element_text(size=10),
        axis.title.y = element_blank(),
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7)) +
  facet_grid(rows = vars(who_region),
             scales = "free",
             space = "free")
```

#
##### World Data
```{r echo=TRUE}

world_filter <- c("Brazil", "United States", "Spain", "Italy", "France", "United Kingdom", 
                  "South Korea", "Mexico", "Iran", "Japan", "Germany", "South Africa", 
                  "Russia", "Ecuador","Canada", "China", "Singapore")

world_cases <- cases %>% 
  filter(location %in% world_filter)

world_deaths <- deaths %>% 
  filter(location %in% world_filter)

world_tests <- tests %>% 
  filter(location %in% world_filter)
```

#### Cohort New Cases (since 100th case)

```{r echo=TRUE}
world_cases %>%  
  ggplot(mapping = aes(x = day, 
                       y = new_cases, 
                       group = location,
                       colour = who_region)) +
  scale_y_log10() + 
  stat_smooth(se=FALSE, span = 0.3) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```

#### Cohort Total Cases (since 100th case)

```{r echo=TRUE}

growth_cases <- cases %>% 
  select(day, location) %>% 
  filter(day > 0,
         location == "World") %>% 
  group_by(day) %>% 
  mutate(doubling_every_day = as.numeric(round(100*2^(day),0)),
         doubling_every_2_days = as.numeric(round(100*2^(day/2),0)),
         doubling_every_4_days = as.numeric(round(100*2^(day/4),0)),
         doubling_every_7_days = as.numeric(round(100*2^(day/7),0)),
         doubling_every_14_days= as.numeric(round(100*2^(day/14),0))) %>% 
  pivot_longer(c(doubling_every_day : doubling_every_14_days),
               names_to = "doubling",
               values_to = "cases") %>% 
  select(day,doubling,cases) %>% 
  filter(cases <= max(world_cases['total_cases']))


world_cases %>% 
  ggplot() +
  scale_y_log10() + 
  geom_line(world_cases,
            mapping = aes(x = day, 
                       y = total_cases, 
                       group = location,
                       colour = who_region), 
            alpha = 0.6, 
            size = 1.2) +
  geom_dl(world_cases,
          mapping = aes(x = day, 
                       y = total_cases,
                       label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  geom_line(growth_cases,
            mapping = aes(x = day,
                          y = cases,
                          group = doubling),
            color = 'gray',
            linetype = 'dashed',
            size = 1) +
  geom_dl(growth_cases,
          mapping = aes(x = day,
                        y = cases,
                        label = doubling), 
          method = list(dl.combine("last.points"), 
                        cex = 0.7), 
          color = "Gray") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7)) +
  labs(x = "Number of days since 100th case",
       y = "Cumulative number of cases")

```

```{r}
world_cases %>% 
  ggplot(mapping = aes(x = day, 
                       y = total_cases_per_million, 
                       group = location,
                       colour = who_region)) +
  scale_y_log10() + 
  geom_line(alpha = 0.6, 
            size = 1.2) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```


#### Cohort new deaths (since 5th death)

```{r echo=TRUE}
world_deaths %>% 
  ggplot(mapping = aes(x = day, 
                       y = new_deaths, 
                       group = location,
                       colour = who_region)) +
  scale_y_log10() + 
  geom_line(alpha = 0.2) +
  geom_smooth(se = FALSE, span = 0.6) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```

#### Cohort total deaths (since 5th death)

```{r echo=TRUE}
growth_deaths <- deaths %>% 
  select(day, location) %>% 
  filter(day > 0,
         location == "World") %>% 
  group_by(day) %>% 
  mutate(doubling_every_day = as.numeric(round(5*2^(day),0)),
         doubling_every_2_days = as.numeric(round(5*2^(day/2),0)),
         doubling_every_4_days = as.numeric(round(5*2^(day/4),0)),
         doubling_every_7_days = as.numeric(round(5*2^(day/7),0)),
         doubling_every_14_days = as.numeric(round(5*2^(day/14),0))) %>% 
  pivot_longer(c(doubling_every_day : doubling_every_14_days),
               names_to = "doubling",
               values_to = "deaths") %>% 
  select(day, doubling, deaths) %>% 
  filter(deaths <= max(world_deaths['total_deaths']))


world_deaths %>% 
  ggplot() +
  scale_y_log10() + 
  geom_line(world_deaths,
            mapping = aes(x = day, 
                       y = total_deaths, 
                       group = location,
                       colour = who_region), 
            alpha = 0.6, 
            size = 1.2) +
  geom_dl(world_deaths,
          mapping = aes(x = day, 
                       y = total_deaths,
                       label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  geom_line(growth_deaths,
            mapping = aes(x = day,
                          y = deaths,
                          group = doubling),
            color = 'gray',
            linetype = 'dashed',
            size = 1,
            alpha = 0.7) +
  geom_dl(growth_deaths,
          mapping = aes(x = day,
                        y = deaths,
                        label = doubling), 
          method = list(dl.combine("last.points"), 
                        cex = 0.7), 
          color = "Gray") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7)) +
  labs(x = "Number of days since 5th death",
       y = "Cumulative number of deaths")
```

```{r}
world_deaths %>% 
  ggplot(mapping = aes(x = day, 
                       y = total_deaths_per_million, 
                       group = location,
                       colour = who_region)) +
  scale_y_log10() + 
  geom_line(alpha = 0.6, size = 1.2) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```

#### Cohort Rate

```{r echo=TRUE}
world_deaths %>% 
  ggplot(mapping = aes(x = day, 
                       y = rate, 
                       group = location,
                       colour = who_region)) +
  scale_y_log10() + 
  geom_line(alpha = 0.6, size = 1.2) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```

#### Cohort Tests

```{r}
world_tests %>% 
  ggplot(mapping = aes(x = day, 
                       y = total_tests, 
                       group = location,
                       colour = tests_units)) +
  scale_y_log10() + 
  geom_line(alpha = 0.6, 
            size = 1.2) +
  geom_point(alpha = 0.6) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  theme(legend.position = "bottom",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```

```{r}
world_tests %>% 
  ggplot(mapping = aes(x = day, 
                       y = total_tests_per_thousand, 
                       group = location,
                       colour = tests_units)) +
  scale_y_log10() + 
  geom_line(alpha = 0.6, 
            size = 1.2) +
  geom_point(alpha = 0.6) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  theme(legend.position = "bottom",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```


#
## America Continent
#
```{r echo=TRUE}

america_filter <- c("Brazil", "United States", "Argentina", "Chile", "Uruguay", "Paraguay",
                    "Peru", "Mexico", "Ecuador", "Canada", "Colombia", "Bolivia")

america_cases <- cases %>% 
  filter(location %in% america_filter)

america_deaths <- deaths %>% 
  filter(location %in% america_filter)

america_tests <- tests %>% 
  filter(location %in% america_filter)
```

#### Difference between actual and max case day

```{r echo=TRUE, fig.width=7, fig.height=7}
day_compare %>% 
  filter(who_region == "Americas") %>%
  left_join(max_cases, by = c("location" = "location")) %>% 
  pivot_longer(c(day,max_cases_day),names_to = "type", values_to = "day") %>% 
  ggplot(mapping = aes(x = day, y = fct_reorder(location,day), colour = who_region)) +
  geom_point(aes(shape = type),
             size = 3) + 
  geom_line(alpha = 0.5, 
            linetype = "dashed",
            size = 1)+
  scale_x_continuous(breaks = seq(0, 100, by = 7)) +
  theme(axis.text.y = element_text(size = 10),
        axis.title.y = element_blank(),
        panel.grid.minor = element_blank())
```

#### Cohort new cases (since 100th case)

```{r echo=TRUE}
america_cases %>% 
  ggplot(mapping = aes(x = day, 
                       y = new_cases, 
                       colour = location)) +
  scale_y_log10() + 
  stat_smooth(se=FALSE, span = 1) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```

#### Cohort total cases (since 100th case)

```{r echo=TRUE}
america_cases %>% 
  ggplot() +
  scale_y_log10() + 
  geom_line(america_cases,
            mapping = aes(x = day, 
                       y = total_cases, 
                       group = location,
                       colour = location), 
            alpha = 0.6, 
            size = 1.2) +
  geom_dl(america_cases,
          mapping = aes(x = day, 
                       y = total_cases,
                       label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  geom_line(growth_cases,
            mapping = aes(x = day,
                          y = cases,
                          group = doubling),
            color = 'gray',
            linetype = 'dashed',
            size = 1) +
  geom_dl(growth_cases,
          mapping = aes(x = day,
                        y = cases,
                        label = doubling), 
          method = list(dl.combine("last.points"), 
                        cex = 0.7), 
          color = "Gray") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7)) +
  labs(x = "Number of days since 100th case",
       y = "Cumulative number of cases") +
  xlim(0, max(america_cases$day))
```

```{r}
america_cases %>% 
  ggplot(mapping = aes(x = day, 
                       y = total_cases_per_million, 
                       colour = location)) +
  scale_y_log10() + 
  geom_line(alpha = 0.8, size = 1.2) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```

#### Cohort new deaths (since 5th death)

```{r echo=TRUE}
america_deaths %>% 
  ggplot(mapping = aes(x = day, 
                       y = new_deaths, 
                       colour = location)) +
  scale_y_log10() +
  geom_smooth(se=FALSE, span = 1) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```

#### Cohort total deaths (since 5th death)

```{r echo=TRUE}
america_deaths %>% 
  ggplot() +
  scale_y_log10() + 
  geom_line(america_deaths,
            mapping = aes(x = day, 
                       y = total_deaths, 
                       group = location,
                       colour = location), 
            alpha = 0.6, 
            size = 1.2) +
  geom_dl(america_deaths,
          mapping = aes(x = day, 
                       y = total_deaths,
                       label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  geom_line(growth_deaths,
            mapping = aes(x = day,
                          y = deaths,
                          group = doubling),
            color = 'gray',
            linetype = 'dashed',
            size = 1,
            alpha = 0.7) +
  geom_dl(growth_deaths,
          mapping = aes(x = day,
                        y = deaths,
                        label = doubling), 
          method = list(dl.combine("last.points"), 
                        cex = 0.7), 
          color = "Gray") +
  
  theme(legend.position = "none",
        axis.line = element_line(size=1, 
                                 colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7)) +
  labs(x = "Number of days since 5th death",
       y = "Cumulative number of deaths") +
  xlim(0, max(america_deaths$day))
```

```{r}
america_deaths %>% 
  ggplot(mapping = aes(x = day, 
                       y = total_deaths_per_million, 
                       colour = location)) +
  scale_y_log10() + 
  geom_line(alpha = 0.8, size = 1) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.8), 
          color = "Black") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```

```{r}

```


```{r}
america_tests %>% 
  ggplot(mapping = aes(x = day, 
                       y = total_tests_per_thousand, 
                       group = location,
                       colour = tests_units)) +
  scale_y_log10() + 
  geom_line(alpha = 0.8, size = 1) +
  geom_point(alpha =0.8) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.8), 
          color = "Black") +
  theme(legend.position = "bottom",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```

## Nordic Countries

```{r}

nordic_filter <- c("Sweden", "Norway", "Denmark", "Finland")

nordic_cases <- cases %>% 
  filter(location %in% nordic_filter)

nordic_deaths <- deaths %>% 
  filter(location %in% nordic_filter)

nordic_tests <- tests %>% 
  filter(location %in% nordic_filter)
```

```{r echo=TRUE}
day_compare %>% 
  filter(location %in% nordic_filter) %>%
  left_join(max_cases, by = c("location" = "location")) %>% 
  pivot_longer(c(day,max_cases_day),
               names_to = "type", 
               values_to = "day") %>% 
  ggplot(mapping = aes(x = day, 
                       y = fct_reorder(location,day), 
                       colour = location)) +
  geom_point(aes(shape = type),
             size = 3) + 
  geom_line(alpha = 0.5, 
            linetype = "dashed",
            size = 1)+
  scale_x_continuous(breaks = seq(0, 100, by = 15)) +
  theme(axis.text.y = element_text(size = 15),
        axis.title.y = element_blank(),
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```

```{r echo=TRUE}
nordic_cases %>%  
  ggplot(mapping = aes(x = day, 
                       y = new_cases, 
                       group = location,
                       colour = location)) +
  scale_y_log10() + 
  stat_smooth(se=FALSE, span = 0.3) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```

```{r echo=TRUE}
nordic_cases %>% 
  ggplot(mapping = aes(x = day, 
                       y = total_cases, 
                       group = location,
                       colour = location)) +
  scale_y_log10() + 
  geom_line(alpha = 0.6, 
            size = 1.2) +
  geom_point(alpha = 0.6) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))

```

```{r}
nordic_cases %>% 
  ggplot(mapping = aes(x = day, 
                       y = total_cases_per_million, 
                       group = location,
                       colour = location)) +
  scale_y_log10() + 
  geom_line(alpha = 0.6, 
            size = 1.2) +
  geom_point(alpha = 0.6) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```


#### Cohort new deaths (since 5th death)

```{r echo=TRUE}
nordic_deaths %>% 
  ggplot(mapping = aes(x = day, 
                       y = new_deaths, 
                       group = location,
                       colour = location)) +
  scale_y_log10() + 
  geom_line(alpha = 0.2) +
  stat_smooth(se=FALSE, 
              span = 0.5) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```

#### Cohort total deaths (since 5th death)

```{r echo=TRUE}
nordic_deaths %>% 
  ggplot(mapping = aes(x = day, 
                       y = total_deaths, 
                       group = location,
                       colour = location)) +
  #scale_y_log10() + 
  geom_line(alpha = 0.6, size = 1.2) +
  geom_point(alpha = 0.6) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```

```{r}
nordic_deaths %>% 
  ggplot(mapping = aes(x = day, 
                       y = total_deaths_per_million, 
                       group = location,
                       colour = location)) +
  #scale_y_log10() + 
  geom_line(alpha = 0.6, size = 1.2) +
  geom_point(alpha = 0.6) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  theme(legend.position = "none",
        panel.grid.minor = element_blank()) +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```


```{r}
nordic_tests %>% 
  ggplot(mapping = aes(x = day, 
                       y = total_tests, 
                       group = location,
                       colour = tests_units)) +
  scale_y_log10() + 
  geom_line(alpha = 0.6, 
            size = 1.2) +
  geom_point(alpha = 0.6) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```

```{r}
nordic_tests %>% 
  ggplot(mapping = aes(x = day, 
                       y = total_tests_per_thousand, 
                       group = location,
                       colour = tests_units)) +
  scale_y_log10() + 
  geom_line(alpha = 0.6, 
            size = 1.2) +
  geom_point(alpha = 0.6) +
  geom_dl(aes(label = location), 
          method = list(dl.combine("last.points"), 
                        cex = 0.9), 
          color = "Black") +
  scale_x_continuous(breaks = seq(0, 100, by = 7))
```